---
title: "03_Cluster_Cells"
author: "Simone Zaghen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    toc: true
    number_section: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../results/") })

---

Based on the bootstrapping results, here we want to check how many cells are in each of the potential clusters we will define. We want to know how many cells are in each cluster in order not to lose statistical power if too few cells are clustered together. Once we cluster cells based on cell cycle and time in the cell cycle, we will move on and do intra-cluster analysis to check which genes are the most variable in each cluster. 

# Load packages

```{r, results='hide', message=FALSE}
#Load packages from CRAN
library(tidyverse)
library(reshape2)
library(Seurat)
library(conflicted)
library(RColorBrewer)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("mutate", "dplyr")

if (!dir.exists("../results/Cluster_Cells")){dir.create("../results/Cluster_Cells/")}

```

# Load dataset and filter data 

```{r, results='hide', message=FALSE}
rawdata <- read_tsv("../data/2021_RAPA_TIMECOURSE.tsv.gz") #load raw data
metadata <- read_tsv("../data/Cell_Cycle_Metadata_01112024.tsv.gz") #cell cycle data

```

Do some data wrangling

```{r}
df <- cbind(rawdata, metadata) #merge data and metadata

df <- df %>%
  filter(Pool %in% c("1", "2")) %>% #timepoints before rapamycin treatment
  filter(Gene %in% "WT") %>% #only wt strain
  drop_na()

```

Prepare the inputs for seurat 

```{r}
counts <- select(df, 1:5843) #exclude the metadata
counts <- as.data.frame(t(counts)) #Seurat: rows as genes, columns as cell
colnames(counts) <- str_remove(colnames(counts), "V") #fix colnames

meta <- select(df, 5844:5849) #retain metadata 

```

Create seurat object

```{r}
#Only load things after filtering so it's faster
srat <- CreateSeuratObject(counts, 
                           project = "cerevisiae",
                           min.cells = 5,
                           min.features = 300)
srat <- AddMetaData(srat, meta)

rm(list = c("counts", "meta", "metadata"))

```

# Normalize and scale data

Remove cells with very low or suspiciously high nCount_RNA (number of UMI reads detected per cell).

```{r}
srat <- subset(srat, subset = nFeature_RNA > 200 & nFeature_RNA < 2400)

```

Normalize data using the relative count (RC) method since it is similar to the normalization method used in previous scripts. (Normalizing with the RC method: "counts for each cell are divided by the total counts for that cell and multiplied by the scale.factor")

```{r}
srat <- NormalizeData(srat, 
                      normalization.method = "RC",
                      scale.factor = 10000,
                      verbose = F)
```

Find the most variable genes (required for pca). 

Using the method "vst" since it is a method similar to the previouis step in which I checked the coefficient of variation for each gene in the dataset. 
vst method: "first, fits a line to the relationship of log(variance) and log(mean) using local polynomial regression (loess). Then standardizes the feature values using the observed mean and expected variance (given by the fitted line). Feature variance is then calculated on the standardized values after clipping to a maximum (see clip.max parameter)."

```{r}
srat <- FindVariableFeatures(srat, 
                             selection.method = "vst", 
                             nfeatures = 3000,
                             verbose = F)

```

Scale data so that average for all of them is 0. 

```{r}
all.genes <- rownames(srat)
srat <- ScaleData(srat, 
                  features = all.genes, 
                  verbose = F)

```

Create discrete time intervals that can be used to color clusters of cells

```{r}
srat@meta.data <- srat@meta.data %>%
  mutate(max = max(Cell_Cycle_Time), 
         min = min(Cell_Cycle_Time), 
         width = (max-min)/30, 
         bin1 = ceiling((Cell_Cycle_Time-min)/width),
         time_interval = ifelse(Cell_Cycle_Time==min, bin1 + 1, bin1),
         time_interval = time_interval * 3) %>%
  select(-c("max", "min", "width", "bin1")) %>%
  mutate(Cell_Cycle_Phase = as.factor(Cell_Cycle_Phase)) %>% #order cell cycle
  mutate(Cell_Cycle_Phase = fct_relevel(Cell_Cycle_Phase,
                                        c("G1", "S", "G2", "M", "M-G1")))

```

# PCA

```{r}
srat <- RunPCA(srat, 
               features = VariableFeatures(object = srat),
               verbose = F)

```

Elbow plot for ranking of principle components based on the percentage of variance explained by each one. 

```{r}
ElbowPlot(srat, ndims = 30)

```

The first 7 PCs explain most of the variation in the data, therefore I will include only those in the next steps. 

```{r, fig.width=6, fig.height=16}
VizDimLoadings(srat, dims = 1:7, reduction = "pca")

```

```{r, }
DimHeatmap(srat, dims = 1, cells = 500, balanced = TRUE)
DimHeatmap(srat, dims = 1:7, cells = 500, balanced = TRUE)

```

PCA plot, faceted by metadata infos

```{r, fig.show='hold'}
DimPlot(srat, reduction = "pca", group.by = "Replicate")
DimPlot(srat, reduction = "pca", group.by = "Pool")
DimPlot(srat, reduction = "pca", group.by = "Experiment")
DimPlot(srat, reduction = "pca", group.by = "Cell_Cycle_Phase")

```


Export figures for paper 

```{r, warning=FALSE, message=FALSE}
#calculate explained variance
pca_var <- Stdev(srat, reduction = "pca")^2
pca_var_percent <- round(pca_var / sum(pca_var) * 100, 2)
x_label <- paste0("PC1 (", pca_var_percent[1], "%)")
y_label <- paste0("PC2 (", pca_var_percent[2], "%)")

#Cell cycle phase
pdf("../results/Cluster_Cells/Cell_Cycle_Phase.pdf", width = 5, height = 4)
DimPlot(srat, 
        reduction = "pca", 
        group.by = "Cell_Cycle_Phase") +
  scale_color_manual(
    values = brewer.pal(5, "Set2")) +
  coord_fixed() +
  scale_x_continuous(name = x_label,
                     limits = c(-15, 15)) +
  scale_y_continuous(name = y_label,
                     limits = c(-15, 15)) +
  theme(legend.position = "none")
dev.off()

#Time in the cell cycle
pdf("../results/Cluster_Cells/Cell_Cycle_Time.pdf", width = 5, height = 4)
FeaturePlot(object = srat, 
            features = "Cell_Cycle_Time") +
  scale_color_viridis_c(option = "magma",
                        direction = -1) +
  coord_fixed() +
  scale_x_continuous(name = x_label,
                     limits = c(-15, 15)) +
  scale_y_continuous(name = y_label,
                     limits = c(-15, 15)) +
  theme(legend.position = "none")
dev.off()

```

# UMAP

I will use the first 7 dims (from the elbow plot we can see that after the 7th dimension the PCs do not explain variation anymore)

```{r}
srat <- FindNeighbors(srat, dims = 1:7)
srat <- FindClusters(srat, resolution = 0.5)

```

```{r}
srat <- RunUMAP(srat, dims = 1:7)
DimPlot(srat, reduction = "umap")

```

```{r, fig.show='hold'}
DimPlot(srat, reduction = "umap", group.by = "Replicate")
DimPlot(srat, reduction = "umap", group.by = "Pool")
DimPlot(srat, reduction = "umap", group.by = "Experiment")
DimPlot(srat, reduction = "umap", group.by = "Cell_Cycle_Phase")
DimPlot(srat, reduction = "umap", group.by = "time_interval")

```

# Conclusions

Both the PCA and the UMAP show that cells cluster well based on cell cycle phase and time. In this script I calculated timeframes of 3 minutes each, and assigned a timeframe to each cell. After checking that clustering cells in 3 minutes timeframes is fine, I can do intra-cluster analysis to check which genes are driving cell variability in each cluster. 
