---
title: "05_Intra-cluster analysis for every timepoint"
author: "Simone Zaghen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    toc: true
    number_section: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../results/") })

---

# Load packages

```{r, results='hide', message=FALSE}
#Load packages from CRAN
library(tidyverse)
#library(reshape2)
library(ggpubr)
library(biomaRt)
library(readxl)
library(conflicted)

#Solve conflicts
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("intersect", "base")

options(dplyr.summarise.inform = FALSE)

```

# Load data 

```{r, results='hide', message=FALSE}
rawdata <- read_tsv("../data/2021_RAPA_TIMECOURSE.tsv.gz") #load raw data
metadata <- read_tsv("../data/Cell_Cycle_Metadata_01112024.tsv.gz") #cell cycle data

#load gene info
ensembl <- useMart(biomart = "ENSEMBL_MART_ENSEMBL",
                   dataset = "scerevisiae_gene_ensembl") 

gen_des <- getBM(attributes = c("ensembl_gene_id",
                                "description",
                                "external_gene_name"),
                 mart = ensembl)

colnames(gen_des) <- c("genes", 
                       "description",
                       "common_name")

rm("ensembl")

```

# Data wrangling

Divide cells into 3 minutes bins and transform df into list

```{r}
df <- cbind(rawdata, metadata) #merge data and metadata

#merge timepoints 2 by 2 to get enough cells in each bin
df$Pool <- str_replace_all(df$Pool, c("1" = "2", 
                                      "3" = "4", 
                                      "5" = "6", 
                                      "7" = "8"))

df <- df %>%
  filter(Gene %in% "WT") %>% #only wt strain
  drop_na() %>% #remove empty levels
  mutate(max = max(Cell_Cycle_Time), #divide cells in time bins
         min = min(Cell_Cycle_Time),
         width = (max-min)/30,
         bin1 = ceiling((Cell_Cycle_Time - min)/width),
         time_interval = ifelse(Cell_Cycle_Time == min, 
                                bin1 + 1, 
                                bin1),
         time_interval = time_interval * 3) %>% #each bin should reflect minutes
  select(-c("max", "min", "width", "bin1")) %>%
  mutate(time_interval = factor(time_interval)) %>%
  group_split(Pool) #split into groups

#assign names to list elements
names(df) <- 1:length(df) #mock names to make loop work
for (i in 1:length(df)) { 
  names(df)[i] <- unique(df[[i]]$Pool) #assign correct names
}

```

# Check how many cells we have in each bin

```{r}
for (i in 1:length(df)) {
  tmp <- df[[i]] %>%
    count(time_interval) %>% 
    ggplot(aes(x = time_interval,
                     y = n)) +
    geom_bar(stat = "identity") +
    ylab("#cells") +
    ggtitle(paste0("Timepoint ", names(df[i])))
  print(tmp)
}

```

In some timepoints I have a very low number of cells - still continuing with the code but this should be discussed and need to be aware of it.

# Discard bins with not enough cells

## Remove bins that do not contain enough cells 

Since some bins do not have enough cells to make a proper reliable linear model to calculate residuals, I remove those bins from the analysis.

```{r}
#get the mininum amount of cells in timeponts 1 and 2
X <- as.numeric(min(table(df$`2`$time_interval)))

df <- df %>%
  map(~.x %>%
        group_by(time_interval) %>%
        filter(n() >= X) %>%
        droplevels() %>%
        ungroup())

rm(X)

```

## Check which bins have been removed

```{r}
for (i in 1:length(df)){
  print(paste0("Bins removed in timepoint", 
               names(df)[i],
               ":"))
  print(setdiff(levels(df$`2`$time_interval),
                       levels(df[[i]]$time_interval)))
}
```

# Intra cluster for each timepoint

## Perform intracluster analysis 

```{r}
intracluster_output <- list()

for (j in 1:length(df)) {
  
  tmp2 <- df[[j]] #select df to work on 

  #define lists to store output
  tmp_model_list <- list()
  tmp_stats_list <- list()
  tmp_plot_list <- list()
  
    for (i in 1:length(levels(tmp2$time_interval))) { #iterate each time bin

    #Create dataframe for specific timepoint
      tmp <- tmp2 %>%
        filter(time_interval %in% levels(tmp2$time_interval)[i]) %>%
        select(-c("Gene", "Replicate", "Pool", "Experiment", "Cell_Cycle_Phase",
                  "Cell_Cycle_Time", "time_interval")) %>%
        filter(rowSums(.) < 15000) #remove cells with counts above 15000
    
      tmp <- tmp*10000/rowSums(tmp) #normalize df
  
    #calculate mean, sd, and coefficient of variation
      tmp_stats <- as.data.frame(t( #transpose to make df ggplot friendly
        rbind(mean = apply(tmp, 2, mean, na.rm = T),
              sd = apply(tmp, 2, sd, na.rm = T),
              CV = (apply(tmp, 2, sd))/(apply(tmp, 2, mean, na.rm = T))))) %>%
        filter(mean > 0.01) %>% #remove low expr
        drop_na() #drop empty levels

    #fit the model
      tmp_model <- lm(log10(CV) ~ log10(mean), 
                      data = tmp_stats, 
                      row.names(tmp_stats$genes))

    #calculate residuals for each gene and adjust them
      tmp_residuals <- data.frame(row.names = names(tmp_model$residuals), 
                                  residuals = tmp_model$residuals)
                
      tmp_stats <- merge(tmp_stats, 
                         tmp_residuals, 
                         by = "row.names") %>%
        rename("genes" = "Row.names") %>%
        merge(gen_des, by = "genes") %>%
        distinct() %>% #only keep unique rows
        arrange(desc(residuals)) %>%
        relocate(common_name, .after = genes)

    #create model plot
      tmp_plot <-
        tmp_stats %>%
        ggplot(aes(x = log10(mean),
                 y = log10(CV))) +
        geom_point() +
        geom_abline(slope = coef(tmp_model)[["log10(mean)"]], 
                    intercept = coef(tmp_model)[["(Intercept)"]],
                    color = "red",
                    linewidth = 1) +
        ggtitle(paste0(
          levels(tmp$time_interval)[i],
          " minutes",
          "_log of x and y, mean > 0.01"))

    #Save outputs
    tmp_model_list[[levels(tmp2$time_interval)[i]]] <- tmp_model #save model
    tmp_stats_list[[levels(tmp2$time_interval)[i]]] <- data.frame(tmp_stats) #save stats
    tmp_plot_list[[levels(tmp2$time_interval)[i]]] <- tmp_plot #save stats

    } #ends iteration in each time bin
  
  #rank combine
  
    #find genes common in all time bins
    tmp_common_genes <- Reduce(intersect, 
                               lapply(tmp_stats_list, 
                                      function(x) {x$genes}))
    
    #calculate rank
    tmp_rank_combine <- 
      tmp_stats_list %>%
      map(~.x %>%
            filter(genes %in% tmp_common_genes) %>% #only keep genes in all timepoints
            drop_na() %>%
            mutate(rank = rank(residuals)) %>% #rank based on non-adjusted residuals
            select(c("genes", "common_name", "rank", "description"))) %>%
      map2(names(tmp_stats_list), ~.x %>% 
             mutate(Time_Point = .y) %>% #add time column
             mutate(Time_Point = as.numeric(Time_Point))) %>% #convert time to num
      bind_rows() %>%
      group_by(genes, common_name, description) %>% 
      summarise(rank_combined = sum(rank)) %>%
      arrange(desc(rank_combined)) #arrange from highest to lowest

    
  #Save results in main list
  intracluster_output[[names(df)[[j]]]] <- list(
    model = tmp_model_list,
    stats = tmp_stats_list,
    plot = tmp_plot_list,
    rank = tmp_rank_combine)
  
  }

rm(list=ls(pattern="^tmp"))

```

## Scale rank across sampling points

Some samples do not have all the timebins - therefore the maximum or minimum possible rank is different than the ones that have more bins. To correct for this, scale the rank so that all the ranks are in the same interval

```{r}
scale_values <- function(x){
  (x-min(x))/(max(x)-min(x))
  }

for (i in 1:length(intracluster_output)) {
  intracluster_output[[i]]$rank$rank_combined <-
    scale_values(intracluster_output[[i]]$rank$rank_combined)
}

```

# Plot the most variable genes over the experiment

```{r, fig.width=6, fig.height=8}
for (i in 1:length(intracluster_output)) {
  
  genes_to_plot <- as.character(intracluster_output[[i]]$rank$genes[1:30])
  title <- paste("Sampling point",
                 names(intracluster_output)[[i]])

  toplot <- intracluster_output %>%
    map(~ pluck(.x, "rank")) %>%
    map2(names(intracluster_output), ~.x %>% 
           mutate(time_bin = .y,
                  time_bin = as.numeric(time_bin))) %>% #add time bin col
    map(~ filter(.x, #only keep genes in the cell_cycle_genes vector
                 genes %in% unique(grep(paste(genes_to_plot,
                                              collapse="|"),
                                              genes,
                                              value = T)))) %>%
    bind_rows() %>%
    mutate(gene = paste(common_name, genes, sep = "|")) %>% #use both genes names
    mutate(gene = factor(gene, levels = unique(gene))) %>% #convert to levels
    ungroup() %>%
    select(c("rank_combined","time_bin", "gene"))

  print(toplot %>% 
    ggplot(aes(x = time_bin,
               y = rank_combined,
               #group = gene,
               color = gene
               )) + 
    geom_line(linewidth = 2) + 
    ggtitle(title) +
    ylim(0,max(toplot$rank_combined)) +
    xlab("Sampling Point") +
    theme(legend.position = "none") +
    facet_wrap(~ gene, ncol = 5)
  )

}
```

# Export data

```{r}
saveRDS(intracluster_output,
        file = "../results/intracluster_analysis_output.Rds")
```

