---
title: "04_Intra-cluster variance analysis"
author: "Simone Zaghen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    toc: true
    number_section: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../results/") })

---

After bootstrapping, we saw that as long as we have approx. 800/1000 cells in each timebin, the model we fit through those cells is similar enough to the model with all cells (pearson coeff 0.9584293). 

Furthermore, from clustering the cells, we saw that cells do cluster based on cell cycle phase and based on the time along the cell cycle. This is great, but it is a problem since we are investigating cell variance, and most of the variance we are currently finding is cell-cycle related.

To bypass this problem, we divide cells in 3 minutes time intervals. After checking that we have 800/1000 cells in each timebin, we fit a linear model for each bin. We then calculate the residuals for each time bin. To extract the genes that are the most variable across all timebins, we rank genes based on their residuals (decreasing order) and then rank combine genes across timebins (basically sum the rank of genes across different timebing). The higher the rank, the more variable the gene is across the sampling points we have in the data (in this case before rapamycin treatment).

Finally, we plot some high and low variability genes, with their average gene count, residuals, and gene count distribution.

At the very end, we also check gene counts and variability for TSL1 and TPS3 genes. These genes are interesting because they have been shown to have stochastic gene expression ([paper here](https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.1001325))

# Load packages

```{r, results='hide', message=FALSE}
#Load packages from CRAN
library(tidyverse)
library(reshape2)
library(ggpubr)
library(biomaRt)
library(readxl)
library(conflicted)
library(ggExtra, lib.loc = "../../R/x86_64-pc-linux-gnu/4.3/")
library(knitr)
library(kableExtra)
library(tidyheatmaps, lib.loc = "../../R/x86_64-pc-linux-gnu/4.3/")
source("functions/loadNoRapaTreat.R")
library(clusterProfiler, lib.loc = "../../R/x86_64-pc-linux-gnu/4.3/")
library(org.Sc.sgd.db, lib.loc = "../../R/x86_64-pc-linux-gnu/4.3/")

#Solve conflicts
conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")
conflict_prefer("rename", "dplyr")
conflict_prefer("intersect", "base")

#Create directory to save output
if (!dir.exists("../results/IntraCluster_Analysis")){
  dir.create("../results/IntraCluster_Analysis/")}

```

# Load data 

The loadNoRapaTreat takes care of importing rawdata and metadata, merging them, only keeping the wt strain before rapa treatment, assigning timebins to cell, and normalizing the gene counts. Check the function itself for more info.

```{r}
df <- loadNoRapaTreat(rawdata_path = "../data/2021_RAPA_TIMECOURSE.tsv.gz",
                      metadata_path = "../data/Cell_Cycle_Metadata_01112024.tsv.gz")

gen_des <- readRDS("../results/Gene_Variance/gensets_and_description.Rds") %>%
  select(-c("gene_Set"))

```

Check how many cells we have in each bin to make sure we have at least 800/100 minimum

```{r}
tmp <- df %>%
  count(time_interval)
tmp %>%
  ggplot(aes(x = time_interval,
                   y = n)) +
  geom_bar(stat = "identity") +
  ylab("#cells")

```

Export data to plot for paper

```{r}
#export #cells in bins
write.csv2(tmp, "../results/IntraCluster_Analysis/cells_in_bins.csv") 

#export top X genes and their expression profile over time
top_genes <- c(unique(read.csv2("../results/Gene_Variance/counts_top_genes.csv")$variable), "YHR087W")
top_counts <- df[1:5843] %>%
  select(all_of(top_genes)) %>%
  cbind(df[5848:5850])
write.csv2(top_counts, "../results/IntraCluster_Analysis/top_counts.csv", row.names = F)

```

# Intra-cluster analysis and plot regression lines

For each bin: calculate mean, standard deviation, and coefficient of variation. Then build a linear model (coefficient of variation vs mean) and calculate the residuals, and adjust them based on the mean. In the past we used adjusted residuals, but we decided not to use them anymore since when the mean is very low, the adj_res becomes very high and 'overpowers' more interesting genes with higher residuals. We still calculated them here to show this effect in a plot. 

```{r}
#define lists to store output
model_list <- list()
stats_list <- list()
plot_list <- list()

for (i in 1:length(levels(df$time_interval))) {

  #Create dataframe for specific timepoint
  tmp <- df %>%
    filter(time_interval %in% levels(df$time_interval)[i]) %>%
    select(-c("Gene", 
              "Replicate", 
              "Pool", 
              "Experiment", 
              "Cell_Cycle_Phase",
              "Cell_Cycle_Time", 
              "time_interval"))
  
  #calculate mean, sd, and coefficient of variation
  tmp_stats <- as.data.frame(t( #transpose to make df ggplot friendly
    rbind(mean = apply(tmp, 2, mean, na.rm = T),
          sd = apply(tmp, 2, sd, na.rm = T),
          CV = (apply(tmp, 2, sd))/(apply(tmp, 2, mean, na.rm = T))))) %>%
    filter(mean > 0.01) %>% #remove very low average expr
    drop_na() #drop empty levels

  #fit the model
  tmp_model <- lm(log10(CV) ~ log10(mean), 
                  data = tmp_stats, 
                  row.names(tmp_stats$genes))

  #calculate residuals for each gene and adjust them
  tmp_residuals <- data.frame(row.names = names(tmp_model$residuals), 
                              residuals = tmp_model$residuals)
                
  tmp_stats <- merge(tmp_stats, 
                     tmp_residuals, 
                     by = "row.names") %>%
    rename("genes" = "Row.names") %>%
    mutate(adj_res = residuals/mean) %>% #adjust residuals
    merge(gen_des, by = "genes") %>%
    distinct() %>% #only keep unique rows
    arrange(desc(adj_res)) %>%
    relocate(common_name, .after = genes)

  #create model plot
  tmp_plot <-
    tmp_stats %>%
    ggplot(aes(x = log10(mean),
             y = log10(CV))) +
    geom_point() +
    geom_abline(slope = coef(tmp_model)[["log10(mean)"]], 
                intercept = coef(tmp_model)[["(Intercept)"]],
                color = "red",
                linewidth = 1) +
    ggtitle(paste0(
      levels(df$time_interval)[i],
      " minutes",
      "_log of x and y, mean > 0.01"))

  #Save oututs
  model_list[[levels(df$time_interval)[i]]] <- tmp_model #save model
  stats_list[[levels(df$time_interval)[i]]] <- data.frame(tmp_stats) #save stats
  plot_list[[levels(df$time_interval)[i]]] <- tmp_plot #save stats
}

rm(list=ls(pattern="^tmp"))

```

Plot the regression lines 

```{r, fig.height=24, fig.width=12}
ggarrange(plotlist = plot_list, ncol=3, nrow =10)

```

# Plot cell cycle genes

As a sanity check, plot both the non-adjusted and the adjusted residuals of cell cycle genes. In the past we used adjusted residuals, but we decided not to use them because when the mean is very low, the adj_res become very high and they 'overpower' more interesting genes with higher residuals. Here they are plotted just to show this effect.

For cell cycle genes, their average expression should "cycle" in the cell cycle, and their residuals should be low since cells are clustered based on three minutes time windows. 

**y scales are different!**

```{r, fig.height=40, fig.width=10}
#import cell cycle annotated genes provided by Chris
cell_cycle_genes <- read_excel("../data/Yeast_Transcriptional_Regulation.xlsx", 
                               sheet = 1) %>%
  rename("Systematic_Name" = "Systematic Name") %>%
  filter(Pathway %in% "Cell Cycle") %>%
  select(c("Pathway", "Systematic_Name", "Gene")) %>%
  filter(Systematic_Name != "#N/A")
cell_cycle_genes <- cell_cycle_genes$Systematic_Name

#plot cell cycle genes
stats_list %>%
  map(~ filter(.x, #only keep genes in the cell_cycle_genes vector
               genes %in% unique(grep(paste(cell_cycle_genes,
                                            collapse="|"),
                                            genes,
                                            value = T)))) %>%
  map2(names(stats_list), ~.x %>% 
         mutate(Time_Point = .y)) %>% #add time column
  bind_rows() %>%
  mutate(Time_Point = as.numeric(Time_Point)) %>%
  select(c("genes", "common_name", "mean", "residuals", "adj_res", "Time_Point")) %>%
  melt(id = c("genes", "common_name", "Time_Point")) %>%
  ggplot(aes(x = Time_Point, #plot
             y = value)) +
  geom_point() +
  scale_x_continuous(breaks = seq(from = 0,
                                  to = 90,
                                  by = 6)) +
  expand_limits(x = 0, y = 0) +
  facet_wrap(common_name ~ variable, 
             scales = "free",
             ncol = 3)
rm("cell_cycle_genes")

```

# Check the mean, residuals, and adjusted residuals distributions in the dataset

```{r, warning=FALSE}
stats_list %>%
  map2(names(stats_list), ~.x %>% 
         mutate(Time_Point = .y)) %>% #add time column
  bind_rows() %>% 
  select(c("genes", "mean", "residuals", "adj_res")) %>%
  melt(id = "genes") %>%
  ggplot(aes(x = value)) +
  geom_density(stat = "density",
               position = "identity") +
    xlim(-2,2) +
    facet_wrap(~variable, 
               scales = "free")
    
```

# Rank combine

First only keep genes common in all time points, then rank the genes in each time bin based on residuals. The lowest rank is assigned to the lowest variable gene in that time bin. Then the ranks for each gene in each time bin are summed together - then extract the genes that rank the highest. These are the genes with the highest variability. Finally we also extract the genes that rank the lowest, which are genes with lowest variability.

```{r, warning=FALSE, message=FALSE}
#calculate rank
rank_combine <- 
  stats_list %>%
  map(~.x %>%
        filter(genes %in% Reduce(intersect, #only keep genes in all timepoints
                                 lapply(stats_list, 
                                        function(x) {
                                          x$genes}))) %>% 
        drop_na() %>%
        mutate(rank = rank(residuals)) %>% #rank based on non-adjusted residuals
        select(c("genes", "common_name", "rank", "description"))) %>%
  map2(names(stats_list), ~.x %>% 
         mutate(Time_Point = .y) %>% #add time column
         mutate(Time_Point = as.numeric(Time_Point))) %>% #convert time to num
  bind_rows() %>%
  group_by(genes, common_name, description) %>% 
  summarise(rank_combined = sum(rank)) %>%
  arrange(desc(rank_combined)) #arrange from highest to lowest

```

# Plot most variable genes

Extract the most variable genes and plot their mean and residuals. Then do a violin plot of their counts over time. 

## Plot mean and residuals for genes with the highest ranks (most variable genes)

```{r, fig.height=60, fig.width=7}
genes_to_plot <- as.character(rank_combine$genes)[3:22] #skips 2 ribosomial genes

stats_list %>%
  map(~ filter(.x, 
               genes %in% unique(grep(paste(genes_to_plot,
                                            collapse="|"),
                                            genes,
                                            value = T)))) %>%
  map2(names(stats_list), ~.x %>% 
         mutate(Time_Point = .y,
                Time_Point = as.numeric(Time_Point))) %>% #add time column
  bind_rows() %>%
  mutate(genes = factor(genes, #sort based on combined residuals
                        levels = genes_to_plot),
         gene = paste(common_name, genes, sep = "|")) %>%
  arrange(match(genes, genes_to_plot)) %>%
  mutate(gene = factor(gene, levels = unique(gene))) %>%
  select(c("gene", "mean", "residuals", "Time_Point")) %>%
  melt(id = c("gene", "Time_Point")) %>%
  ggplot(aes(x = Time_Point, #plot
             y = value)) +
  geom_point() +
    scale_x_continuous(breaks = seq(from = 0,
                                  to = 90,
                                  by = 6)) +
  expand_limits(x = 0, y = 0) +
  facet_wrap(gene ~ variable, 
             scales = "free", 
             ncol = 2)

```

## Do violon plot of gene counts for these genes

```{r, fig.height=64, fig.width=10}
df %>%
  select(c(all_of(genes_to_plot))) %>% #select the most variable genes
  cbind(df[5848:5850]) %>% #keep metadata as well
  melt(id = c("Cell_Cycle_Phase", "Cell_Cycle_Time", "time_interval"),
       value.name = "counts",
       variable.name = "genes") %>% #melt for ggplot
  merge(gen_des %>% select(c("genes", "common_name"))) %>% #get common gene name
  mutate(gene = paste(common_name, genes, sep = "|")) %>% #use both genes names
  arrange(match(genes, genes_to_plot)) %>% #arrange genes based on residuals
  mutate(gene = factor(gene, levels = unique(gene))) %>% #convert to levels
  select(c("time_interval","counts","gene")) %>%
  ggplot(aes(x = time_interval,
             y = counts)) +
  geom_violin() +
    facet_wrap(~gene,
             scales = "free",
             ncol = 1)

```

# Plot the least variable genes

## Plot mean and residuals for genes with the lowest ranks (least variable genes)

```{r, fig.height=60, fig.width=7}
genes_to_plot <- as.character(tail(rank_combine$genes, n = 20))

stats_list %>%
  map(~ filter(.x, 
               genes %in% unique(grep(paste(genes_to_plot,
                                            collapse="|"),
                                            genes,
                                            value = T)))) %>%
  map2(names(stats_list), ~.x %>% 
         mutate(Time_Point = .y,
                Time_Point = as.numeric(Time_Point))) %>% #add time column
  bind_rows() %>%
  mutate(genes = factor(genes, #sort based on combined residuals
                        levels = genes_to_plot),
         gene = paste(common_name, genes, sep = "|")) %>%
  arrange(match(genes, genes_to_plot)) %>%
  mutate(gene = factor(gene, levels = unique(gene))) %>%
  select(c("gene", "mean", "residuals", "Time_Point")) %>%
  melt(id = c("gene", "Time_Point")) %>%
  ggplot(aes(x = Time_Point, #plot
             y = value)) +
  geom_point() +
    scale_x_continuous(breaks = seq(from = 0,
                                  to = 90,
                                  by = 6)) +
  expand_limits(x = 0, y = 0) +
  facet_wrap(gene ~ variable, 
             scales = "free", 
             ncol = 2)

```

## Do violin plot of gene counts for these genes

```{r, fig.height=64, fig.width=10}
df %>%
  select(c(all_of(genes_to_plot))) %>% #select the least variable genes
  cbind(df[5848:5850]) %>% #keep metadata as well
  melt(id = c("Cell_Cycle_Phase", "Cell_Cycle_Time", "time_interval"),
       value.name = "counts",
       variable.name = "genes") %>% #melt for ggplot
  merge(gen_des %>% select(c("genes", "common_name"))) %>% #get common gene name
  mutate(gene = paste(common_name, genes, sep = "|")) %>% #use both genes names
  arrange(match(genes, genes_to_plot)) %>% #arrange genes based on residuals
  mutate(gene = factor(gene, levels = unique(gene))) %>% #convert to levels
  select(c("time_interval","counts","gene")) %>%
  ggplot(aes(x = time_interval,
             y = counts)) +
  geom_violin() +
  facet_wrap(~gene,
             scales = "free",
             ncol = 1)

```

# Plot high variability genes next to low variability genes

Trying to plot high variability next to low variability, I noticed that the low variability are generally on way lower scales/counts.

The goal of this is to visualize how gene counts are distributed for high vs low variability genes.

```{r, fig.height=12, fig.width=10}
tmp <- df %>%
  select(c("YOR383C",  #high var
           "YOR234C", #low var
           "YLR286C", #high var
           "YPL037C", #low var
           "YJL189W", #high var
           "YOR133W") #low var
         ) %>%
  cbind(df[5848:5850]) %>% #keep metadata as well
  melt(id = c("Cell_Cycle_Phase", "Cell_Cycle_Time", "time_interval"),
       value.name = "counts",
       variable.name = "genes") %>% #melt for ggplot
  merge(gen_des %>% select(c("genes", "common_name"))) %>% #get common gene name
  mutate(gene = paste(common_name, genes, sep = "|")) %>% #use both genes names
  mutate(gene = factor(gene, levels = unique(gene))) %>% #convert to levels
  mutate(gene = fct_relevel(gene,
                            c("FIT3|YOR383C",
                              "RPL33B|YOR234C",
                              "CTS1|YLR286C",
                              "EGD1|YPL037C",
                              "RPL39|YJL189W",
                              "EFT1|YOR133W"))) %>%
  select(c("time_interval","counts","gene"))
write.csv2(tmp, 
           "../results/IntraCluster_Analysis/high_vs_low_var_data.csv",
           row.names = F)

tmp %>%
  ggplot(aes(x = time_interval,
             y = counts)) +
  geom_violin() +
  ggtitle("High variability on the left, low variability on the right") +
  facet_wrap(~gene,
             ncol = 2)

```

# Extract genes with low mean and high residuals 

The most interesting genes are those with a very low mean, so overall low expression, but with high residuals. These genes are lowly expressed in most cells, but in some are highly expressed and thus have high variability. These genes are the most interesting for us. 

## Plot their mean and residuals

```{r, fig.height=40, fig.width=10}
tmp <- stats_list %>%
  map(~ filter(.x, mean < 1)) %>% #keep genes with low counts
  map(~ filter(.x, #keep genes with high rank
               genes %in% unique(grep(paste(rank_combine$genes[1:100],
                                            collapse="|"),
                                            genes,
                                            value = T))))
#need to break the pipe to get the common genes out
common_genes <- Reduce(intersect, #get genes present in all timebins 
                       lapply(tmp, 
                              function(x) {
                                x$genes}))

tmp %>%
  map(~ filter(.x, #only keep genes in the all timebins
               genes %in% unique(grep(paste(common_genes,
                          collapse="|"),
                          genes,
                          value = T)))) %>%
  map2(names(stats_list), ~.x %>% 
         mutate(Time_Point = .y,
                Time_Point = as.numeric(Time_Point))) %>% #add time column
  bind_rows() %>%
  mutate(genes = factor(genes, #sort based on combined residuals
                        levels = rank_combine$genes[1:100]),
         gene = paste(common_name, genes, sep = "|")) %>%
  arrange(match(genes, rank_combine$genes[1:100])) %>%
  mutate(gene = factor(gene, levels = unique(gene))) %>%
  select(c("gene", "mean", "residuals", "Time_Point")) %>%
  melt(id = c("gene", "Time_Point")) %>%
  ggplot(aes(x = Time_Point, #plot
             y = value)) +
  geom_point() +
    scale_x_continuous(breaks = seq(from = 0,
                                  to = 90,
                                  by = 6)) +
  expand_limits(x = 0, y = 0) +
  facet_wrap(gene ~ variable, 
             scales = "free", 
             ncol = 2)

```

## Plot their gene counts

```{r, fig.height=40, fig.width=10}
tmp <- df %>%
  select(c(all_of(common_genes))) %>% #select the interesting genes
  cbind(df[5848:5850]) %>% #keep metadata as well
  melt(id = c("Cell_Cycle_Phase", "Cell_Cycle_Time", "time_interval"),
       value.name = "counts",
       variable.name = "genes") %>% #melt for ggplot
  merge(gen_des %>% select(c("genes", "common_name"))) %>% #get common gene name
  mutate(gene = paste(common_name, genes, sep = "|")) %>% #use both genes names
  arrange(match(genes, rank_combine$genes[1:100])) %>% #arrange genes based on residuals
  mutate(gene = factor(gene, levels = unique(gene))) %>% #convert to levels
  select(c("time_interval","counts","gene"))

write.csv2(tmp, 
           "../results/IntraCluster_Analysis/stochastic_genes_counts.csv",
           row.names = F)

tmp %>%
  ggplot(aes(x = time_interval,
             y = counts)) +
  geom_violin() +
  facet_wrap(~gene,
             scales = "free",
             ncol = 1)

```

# TSL1 and TPS3 genes

David is interested in seeing the distribution of TSL1 and TPS3 genes, so plot their mean and residuals. These genes have been shown to have stochastic gene expression in [this paper](https://journals.plos.org/plosbiology/article?id=10.1371/journal.pbio.1001325), that's why we are interested in checking them. 

```{r}
#plot mean expr and residual
stats_list %>%
  map(~ filter(.x, genes %in% c("YML100W", "YMR261C"))) %>%
  map2(names(stats_list), ~.x %>% 
         mutate(Time_Point = .y,
                Time_Point = as.numeric(Time_Point))) %>% #add time column
  bind_rows() %>%
  select(c("common_name", "mean", "residuals", "Time_Point")) %>%
  melt(id = c("common_name", "Time_Point")) %>%
  ggplot(aes(x = Time_Point, #plot
             y = value)) +
  geom_point() +
  scale_x_continuous(breaks = seq(from = 0,
                                  to = 90,
                                  by = 6)) +
  expand_limits(x = 0, y = 0) +
  facet_grid(common_name ~ variable, 
             scales = "free")

```

Plot gene counts

```{r, fig.height=8, fig.width=8}
df %>%
  select(c("YML100W", "YMR261C", "time_interval")) %>% #select the interesting genes
  rename(TSL1_YML100W = YML100W,
         TPS3_YMR261C = YMR261C) %>%
  pivot_longer(cols = !time_interval,
               names_to = "genes") %>%
  ggplot(aes(x = time_interval,
             y = value)) +
  geom_violin() +
  facet_wrap(~genes, ncol = 1)

```

And do a marginal plot

```{r, fig.keep='last', warning=FALSE}
tmp <- df %>%
  select(c("YML100W", "YMR261C")) %>% #select genes
  rename(TSL1_YML100W = YML100W,
         TPS3_YMR261C = YMR261C) %>%
  cbind(df[5848:5850]) %>% #keep metadata as well
  ggplot(aes(x = log10(TSL1_YML100W+1),
             y = log10(TPS3_YMR261C+1))) +
  xlab("TSL1_YML100W") +
  ylab("TPS3_YMR261C") +
  ggtitle("Log10 Scale") +
  geom_point()

ggMarginal(tmp, type = "density")

```

# Save output

```{r}
saveRDS(stats_list,
        file = "../results/IntraCluster_Analysis/stats_list.Rds")
saveRDS(rank_combine,
        file = "../results/IntraCluster_Analysis/rank_combine.Rds")
write.csv2(rank_combine,
        file = "../results/IntraCluster_Analysis/rank_combine.csv",
        row.names = F)

```

# Run GSEA on ranked genes and on stochastic genes

## GSEA on ranked genes

```{r}
gse_res <- list()

original_gene_list <- rank_combine$rank_combined #rank on rank_combined
names(original_gene_list) <- rank_combine$genes # name the vector
gene_list <- na.omit(original_gene_list) # omit any NA values 
gene_list = sort(gene_list, decreasing = TRUE) # sort in decreasing order 

#Run GSEA
gse_res$full_df <- 
  gseGO(geneList = gene_list, 
        ont ="ALL", 
        keyType = "ENSEMBL", 
        minGSSize = 5, 
        maxGSSize = 500, 
        pvalueCutoff = 0.05,
        verbose = T, 
        scoreType = "pos",
        OrgDb = org.Sc.sgd.db, 
        pAdjustMethod = "none")

dotplot(gse_res$full_df, showCategory=15)

```

## GSEA on stochastic genes

```{r, fig.height=10, fig.width=8}
tmp <- stats_list %>%
  map(~ filter(.x, mean < 1)) %>% #keep genes with low counts
  map(~ filter(.x, #keep genes with high rank
               genes %in% unique(grep(paste(rank_combine$genes[1:500],
                                            collapse="|"),
                                            genes,
                                            value = T))))
#need to break the pipe to get the common genes out
common_genes <- Reduce(intersect, #get genes present in all timebins 
                       lapply(tmp, 
                              function(x) {
                                x$genes}))

rank_combine_filtered <- rank_combine %>%
  filter(genes %in% common_genes)

write.csv2(rank_combine_filtered,
           "../results/IntraCluster_Analysis/stochastic_genes.csv",
           row.names = F)

original_gene_list <- rank_combine_filtered$rank_combined #rank on rank_combined
names(original_gene_list) <- rank_combine_filtered$genes #name the vector
gene_list <- na.omit(original_gene_list) #omit any NA values 
gene_list = sort(gene_list, decreasing = TRUE) #sort list

#Run GSEA
gse_res$filtered <- 
  gseGO(geneList = gene_list, 
        ont ="ALL", 
        keyType = "ENSEMBL", 
        minGSSize = 5, 
        maxGSSize = 500, 
        pvalueCutoff = 0.05,
        verbose = T, 
        scoreType = "pos",
        OrgDb = org.Sc.sgd.db, 
        pAdjustMethod = "none")

dotplot(gse_res$filtered, showCategory=15)

```
