---
title: "06_Intra-cluster analysis for every timepoint"
author: "Simone Zaghen"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    toc: true
    number_section: true
    toc_float: 
      collapsed: false
      smooth_scroll: true
knit: (function(inputFile, encoding) {
  rmarkdown::render(inputFile, encoding = encoding, output_dir = "../results/") })

---

Now that we calculated the most variable genes for the sampling point before rapamycin tratment, we want to extend the analysis to all timepoints and check how the most variable geens change over time after rapamycin treatment. 

# Load packages

```{r, results='hide', message=FALSE}
#Load packages from CRAN
library(tidyverse)
library(ggpubr)
library(conflicted)
source("functions/LoadWholeWtDataset.R")

conflicts_prefer(dplyr::filter)
options(dplyr.summarise.inform = FALSE)

#create folders
if (!dir.exists("../results/IntraCluster_AllTimePoints")){
  dir.create("../results/IntraCluster_AllTimePoints/")}

```

# Load data 

Load the full dataset for the wild type strain. The function loadWholeWtDataset takes care of importing data and metadata, normalizing them, and calculating the timebins for each cell in the dataframe (divide cells into 3 minutes timebins). 

```{r, results='hide', message=FALSE}
df <- loadWholeWtDataset(rawdata_path = "../data/2021_RAPA_TIMECOURSE.tsv.gz",
                         metadata_path = "../data/Cell_Cycle_Metadata_01112024.tsv.gz")

#load gene info
gen_des <- readRDS("../results/Gene_Variance/gensets_and_description.Rds") %>%
  select(-c("gene_Set"))

```

Since we don't have many cells per timebin after rapa tratment, we decided to merge sampling timepoints (column Pool) two by two. Then transform df into list (each element is a sampling point) to be able to loop functions through the list. 

```{r}
#merge timepoints 2 by 2 to get enough cells in each bin
df$Pool <- str_replace_all(df$Pool, c("1" = "2", 
                                      "3" = "4", 
                                      "5" = "6", 
                                      "7" = "8"))
df <- split(df , f = df$Pool)

```

# Check how many cells we have in each bin

```{r, fig.show='hold', out.width='25'}
for (i in 1:length(df)) {
  tmp <- df[[i]] %>%
    count(time_interval) %>% 
    ggplot(aes(x = time_interval,
                     y = n)) +
    geom_bar(stat = "identity") +
    ylab("#cells") +
    ggtitle(paste0("Timepoint ", names(df[i])))
  print(tmp)
}

```

# Discard bins with not enough cells

## Remove bins that do not contain enough cells 

In some timepoints, even after merging two sampling points, I have a very low number of cells.
Since some bins do not have enough cells to make a proper reliable linear model to calculate residuals, I remove those bins from the analysis.

```{r}
#get the mininum amount of cells in timeponts 1 and 2
X <- as.numeric(min(table(df$`2`$time_interval)))

#remove timebins with less than those cells
df <- df %>%
  map(~.x %>%
        group_by(time_interval) %>%
        filter(n() >= X) %>%
        droplevels() %>%
        ungroup())

rm(X)

```

## Check which bins have been removed

```{r}
for (i in 1:length(df)){
  print(paste0("Bins removed in timepoint", 
               names(df)[i],
               ":"))
  print(setdiff(levels(df$`2`$time_interval),
                       levels(df[[i]]$time_interval)))
}
```

# Intra cluster for each timepoint

For each sampling point we take each timebin (that remained after removing those without enough cells) - for each timebin we calculate mean, standard deviation, and coefficient of variation. Then we build a linear model (coefficient of variation vs mean) and calculate the residuals. To extract the genes that are the most variable across all timebins, we rank genes based on their residuals (decreasing order) and then rank combine genes across timebins (basically sum the rank of genes across different timebing). The higher the rank, the more variable the gene is across the sampling points we have in the data (in this case before rapamycin treatment).

## Perform intracluster analysis 

```{r}
intracluster_output <- list()

for (j in 1:length(df)) {
  
  tmp2 <- df[[j]] #select df to work on 

  #define lists to store output
  tmp_model_list <- list()
  tmp_stats_list <- list()
  tmp_plot_list <- list()
  
    for (i in 1:length(levels(tmp2$time_interval))) { #iterate each time bin

    #Create dataframe for specific timepoint
      tmp <- tmp2 %>%
        filter(time_interval %in% levels(tmp2$time_interval)[i]) %>%
        select(-c("Gene", "Replicate", "Pool", "Experiment", "Cell_Cycle_Phase",
                  "Cell_Cycle_Time", "time_interval"))

    #calculate mean, sd, and coefficient of variation
      tmp_stats <- as.data.frame(t( #transpose to make df ggplot friendly
        rbind(mean = apply(tmp, 2, mean, na.rm = T),
              sd = apply(tmp, 2, sd, na.rm = T),
              CV = (apply(tmp, 2, sd))/(apply(tmp, 2, mean, na.rm = T))))) %>%
        filter(mean > 0.01) %>% #remove low expr
        drop_na() #drop empty levels

    #fit the model
      tmp_model <- lm(log10(CV) ~ log10(mean), 
                      data = tmp_stats, 
                      row.names(tmp_stats$genes))

    #calculate residuals for each gene and adjust them
      tmp_residuals <- data.frame(row.names = names(tmp_model$residuals), 
                                  residuals = tmp_model$residuals)
                
      tmp_stats <- merge(tmp_stats, 
                         tmp_residuals, 
                         by = "row.names") %>%
        rename("genes" = "Row.names") %>%
        merge(gen_des, by = "genes") %>%
        distinct() %>% #only keep unique rows
        arrange(desc(residuals)) %>%
        relocate(common_name, .after = genes)

    #create model plot
      tmp_plot <-
        tmp_stats %>%
        ggplot(aes(x = log10(mean),
                 y = log10(CV))) +
        geom_point() +
        geom_abline(slope = coef(tmp_model)[["log10(mean)"]], 
                    intercept = coef(tmp_model)[["(Intercept)"]],
                    color = "red",
                    linewidth = 1) +
        ggtitle(paste0(
          levels(tmp2$time_interval)[i],
          " minutes",
          "_log of x and y, mean > 0.01"))

    #Save outputs
    tmp_model_list[[levels(tmp2$time_interval)[i]]] <- tmp_model #save model
    tmp_stats_list[[levels(tmp2$time_interval)[i]]] <- data.frame(tmp_stats) #save stats
    tmp_plot_list[[levels(tmp2$time_interval)[i]]] <- tmp_plot #save stats

    } #ends iteration in each time bin
  
  #rank combine
  
    #find genes common in all time bins
    tmp_common_genes <- Reduce(intersect, 
                               lapply(tmp_stats_list, 
                                      function(x) {x$genes}))
    
    #calculate rank
    tmp_rank_combine <- 
      tmp_stats_list %>%
      map(~.x %>%
            filter(genes %in% tmp_common_genes) %>% #only keep genes in all timepoints
            drop_na() %>%
            mutate(rank = rank(residuals)) %>% #rank based on non-adjusted residuals
            select(c("genes", "common_name", "rank", "description"))) %>%
      map2(names(tmp_stats_list), ~.x %>% 
             mutate(Time_Point = .y) %>% #add time column
             mutate(Time_Point = as.numeric(Time_Point))) %>% #convert time to num
      bind_rows() %>%
      group_by(genes, common_name, description) %>% 
      summarise(rank_combined = sum(rank)) %>%
      arrange(desc(rank_combined)) #arrange from highest to lowest

    
  #Save results in main list
  intracluster_output[[names(df)[[j]]]] <- list(
    model = tmp_model_list,
    stats = tmp_stats_list,
    plot = tmp_plot_list,
    rank = tmp_rank_combine)
  
  }

rm(list=ls(pattern="^tmp"))

```

## Scale rank across sampling points

Some samples do not have all the timebins - therefore the maximum or minimum possible rank is different than the ones that have more bins. To correct for this, scale the rank so that all the ranks are in the same interval

```{r}
scale_values <- function(x){
  (x-min(x))/(max(x)-min(x))
  }

for (i in 1:length(intracluster_output)) {
  intracluster_output[[i]]$rank$rank_combined <-
    scale_values(intracluster_output[[i]]$rank$rank_combined)
}

```

# Plot the most variable genes over the experiment

For each sampling point, I am going to extract the most variable genes (higher scaled rank in that specific sampling point). After extracting those genes, i will fetch their rank across all sampling points and plot the trand to check if the variability associated with that gene increases or decreases. 

```{r, fig.width=6, fig.height=8}
for (i in 1:length(intracluster_output)) {
  
  genes_to_plot <- as.character(intracluster_output[[i]]$rank$genes[1:30])
  title <- paste("Sampling point",
                 names(intracluster_output)[[i]])

  toplot <- intracluster_output %>%
    map(~ pluck(.x, "rank")) %>%
    map2(names(intracluster_output), ~.x %>% 
           mutate(time_bin = .y,
                  time_bin = as.numeric(time_bin))) %>% #add time bin col
    map(~ filter(.x, #only keep genes in the cell_cycle_genes vector
                 genes %in% unique(grep(paste(genes_to_plot,
                                              collapse="|"),
                                              genes,
                                              value = T)))) %>%
    bind_rows() %>%
    mutate(gene = paste(common_name, genes, sep = "|")) %>% #use both genes names
    mutate(gene = factor(gene, levels = unique(gene))) %>% #convert to levels
    ungroup() %>%
    select(c("rank_combined","time_bin", "gene"))

  print(toplot %>% 
    ggplot(aes(x = time_bin,
               y = rank_combined,
               #group = gene,
               color = gene
               )) + 
    geom_line(linewidth = 2) + 
    ggtitle(title) +
    ylim(0,max(toplot$rank_combined)) +
    xlab("Sampling Point") +
    theme(legend.position = "none") +
    facet_wrap(~ gene, ncol = 5)
  )

}
```

# Export data

```{r}
saveRDS(intracluster_output,
        file = "../results/IntraCluster_AllTimePoints/intracluster_analysis_output.Rds")
```

