---
title: "Seurat"
output: html_document
date: "2023-10-23"
---

# Load packages

```{r, results='hide', message=FALSE}
#Install and load packages from bioconductor
if (!require("BiocManager", quietly = TRUE)) install.packages("BiocManager")
if (!require("biomaRt", quietly = TRUE)) install("biomaRt"); library(biomaRt)

#Install and load packages from CRAN
if (!require('tidyverse')) install.packages('tidyverse'); library('tidyverse')
if (!require('reshape2')) install.packages('reshape2'); library('reshape2')
if (!require('Seurat')) install.packages('Seurat'); library('Seurat')


library(conflicted)

conflict_prefer("select", "dplyr")
conflict_prefer("filter", "dplyr")

```

# Load dataset and filter data 

Here I'm loading the dataset from [this paper](https://doi.org/10.1101/2023.09.21.558277).

The dataset can be downloaded from [supplementary data 1](https://zenodo.org/records/8371195).

The dataset "is single-cell response to rapamycin count data deposited in GEO with accession GSE242556. It is a 173348 rows × 5847 columns TSV.GZ file where the first row is a header, the first 5843 columns are integer gene counts, and the final 4 columns ('Gene', 'Replicate', 'Pool', and 'Experiment') are cell-specific metadata."

```{r}
rawdata <- read_tsv("../data/2021_RAPA_TIMECOURSE.tsv.gz") #load raw data
metadata <- read_tsv("../data/Cell_Cycle_Metadata.tsv.gz") #cell cycle data

rawdata <- cbind(rawdata, metadata)

df <- rawdata %>%
  filter(Pool %in% c("2", "8")) %>% #timepoints before rapamycin treatment
  filter(Gene %in% "WT") %>% #only wt strain
  select(1:5843) %>% #exclude the metadata
  drop_na()
df <- as.data.frame(t(df)) #Seurat: rows as genes, columns as cell. Transpose
colnames(df) <- str_remove(colnames(df), "V") #fix colnames removing the V

meta <- rawdata[5844:5847] #retain metadata

```

Create the Seurat object and add the metadata to it

```{r}
#Only load things after filtering so it's faster
srat <- CreateSeuratObject(df, project = "cerevisiae") 
srat <- AddMetaData(srat, meta)

```

```{r}
VlnPlot(srat, 
        features = c("nFeature_RNA","nCount_RNA"),
        ncol = 2, 
        pt.size = 0,
        group.by = "Pool") & 
  theme(plot.title = element_text(size=10))

#nFeature_RNA: number of expressed (detected) genes per same cell
#nCount_RNA: number of UMI reads detected per cell

```

```{r}
FeatureScatter(srat, 
               feature1 = "nCount_RNA", 
               feature2 = "nFeature_RNA",
               group.by = "Pool")

```

```{r}
srat <- NormalizeData(srat)

```


```{r}
srat <- FindVariableFeatures(srat, selection.method = "vst")

top10 <- head(VariableFeatures(srat), 10)
top10 


plot1 <- VariableFeaturePlot(srat)
LabelPoints(plot = plot1, points = top10, repel = TRUE, xnudge = 0, ynudge = 0)


```


```{r}
all.genes <- rownames(srat)
srat <- ScaleData(srat, features = all.genes)

```

```{r}
srat <- RunPCA(srat, features = VariableFeatures(object = srat))
print(srat[["pca"]], dims = 1:5, nfeatures = 5)
VizDimLoadings(srat, dims = 1:2, reduction = "pca")
DimPlot(srat, reduction = "pca") + NoLegend()
DimHeatmap(srat, dims = 1, cells = 500, balanced = TRUE)
DimHeatmap(srat, dims = 1:15, cells = 500, balanced = TRUE)

```

```{r}
ElbowPlot(srat)

```

```{r}
srat <- FindNeighbors(srat, dims = 1:10)
srat <- FindClusters(srat, resolution = 0.5)
head(Idents(srat), 5)

```

```{r}
srat <- RunUMAP(srat, dims = 1:10)
DimPlot(srat, reduction = "umap")

```


```{r}

```




